\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2016-11-29 Response.tex

In addition, an additional sentence was added to highlight the difference in parameters for the experimental results:
\begin{correction}
    The parameters are modified to account for the differences in the hardware model of the hexrotor.
\end{correction}

\item \textit{What are the design parameters of the proposed method and how the design parameters are selected? These should be included in the manuiscript.}

Additional detail has been added to describe the selection of the controller gains and error function parameters. 
This has been described in the response above.

\item \textit{Specification of the sensors in the experiments should be included in the manuscript.}

Additional detail on the sensors and their operation has been included:
\begin{correction}
    Attitude information is measured by a combination of both on and off board sensor systems.
    The VectorNav VN-100 is a rugged, miniature high-performance inertial measurement unit which provides high frequency angular velocity measurements.
    A Vicon motion capture system is installed within the test environment and used to provide high accuracy attitude measurements. 
    A series of reflective markers are placed on the hexrotor and their relative position is captured by a series of infrared optical cameras. 
    Assuming a fixed rigid body, the Vicon system is able to derive the attitude of the hexrotor and transmit this data to the processor onboard the hexrotor.
    The control input is computed on-board, using the full state measurement, and implemented at approximately \SI{100}{\hertz}.
\end{correction}
\end{enumerate}

### 2016-11-29 manuscript.tex
Add more detail about the sensor on the hexrotor
Reviewer 4 #6

\begin{figure}[H]
    \centering
    \includegraphics[width = 0.75\columnwidth]{hexrotor}
    \caption{Attitude control testbed~\label{fig:hexrotor}}
\end{figure}
Attitude information is measured by an onboard IMU and a Vicon motion capture system in the test area.
The control input is computed onboard the hexrotor using data transmitted via WiFi in a client/server model.
In order to constrain the motion, allowing us to test only the attitude dynamics, we attach the hexrotor to a spherical joint.
Since, the center of rotation is below the center of gravity of the hexrotor there is a destabilizing gravitational moment.
The resulting attitude dynamics are similar to an inverted pendulum model.
We augment the control input in~\cref{eqn:adaptive_control} with an additional term to negate the effect of the gravitational moment.

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width = 0.75\columnwidth]{hexrotor}
    \caption{Attitude control testbed~\label{fig:hexrotor}}
\end{figure}
Attitude information is measured by a combination of both on and off board sensor systems.
The VectorNav VN-100 is a rugged, miniature high-performance inertial measurement unit which provides high frequency angular velocity measurements.
A Vicon motion capture system is installed within the test environment and used to provide high accuracy attitude measurements. 
A series of reflective markers are placed on the hexrotor and their relative position is captured by a series of infrared optical cameras. 
Assuming a fixed rigid body, the Vicon system is able to derive the attitude of the hexrotor and transmit this data to the processor onboard the hexrotor.
The control input is computed on-board, using the full state measurement, and implemented at approximately \SI{100}{\hertz}.
In order to constrain the motion, allowing us to test only the attitude dynamics, we attach the hexrotor to a spherical joint.
Since, the center of rotation is below the center of gravity of the hexrotor there is a destabilizing gravitational moment.
The resulting attitude dynamics are similar to an inverted pendulum model.
We augment the control input in~\cref{eqn:adaptive_control} with an additional term to negate the effect of the gravitational moment.
